Insertion Sort Analysis in Java

### 2015-02-04 Programming Project A/Insertion Sort Analysis in Java.tex
added more issues

Another issue encountered during the development of this program was

%% Also mention generics

@@

>>>>

Another issue encountered during the development of this program was executing Java $assert$ statements. When assertions were wrapped in parenthesis, they evaluated to a boolean, and the assert would throw an $AssertionError$ with the explanation 'cannot compare to boolean'. Removing the parenthesis wrapping the assertion fixed this issue.

The last issue encountered during the development process of this program was generic programming. The program would not compile because not all Objects have a compareTo method. Adding the statement $<T$ $extends$ $Comparable<T>>$ fixed this issue.

@@

%% TODO: Cite shit
